---
title: "DevelopingDataProdeuctP1"
output: html_document
date: "Jan, 26, 2020"
---



```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)

```


Intructions

Create a web page using R Markdown that features a map created with Leaflet. 
Host your webpage on either GitHub Pages, RPubs, or NeoCities.
Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity! 


## Location
Selected NY city and top 4 building

```{r chunk 1}
library(leaflet)
lats<-c(40.778384, 40.723430,40.669387, 40.744049)
longs<-c( -73.968258, -73.999568,-73.965259, -73.848336)
places<-c('Central Park', 'Lower Manhattan', 'Brooklyn Botanic Garden','Queen Zoo')
states<-c('Manhattan', 'Manhattan', 'Brooklyn','Queens')
df<-data.frame(lat=lats, lng=longs, places=places, states=states, statecolor=c("blue","blue","yellow","green") )

```

## Including Plot graph
map interactive


```{r chunk 2}
df%>%leaflet()%>%addTiles()%>%addCircleMarkers(color=df$statecolor, popup = df$places) %>% addLegend(labels = states[1:4], colors=c("blue","blue", "yellow","green")) %>% addProviderTiles(providers$OpenStreetMap)

```

